---
title: "Assignment 1"
---

# Assignment 1

```{r}
1 + 1
```

My first assignment has two parts.

## (a)

## **Question:**

Explain the main stages of the Data Science process and state why the Exploratory Data Analysis (EDA) step is important in this process.

**Answer:**\
The data science process generally consists of the following main stages:

1.  **Problem Definition** – Clearly defining the problem that needs to be solved.

2.  **Data Collection and Preparation** – Gathering data from different sources and cleaning it to make it suitable for analysis.

3.  **Exploratory Data Analysis (EDA)** – Performing visualization and statistical analysis to understand the structure of the data.

4.  **Model and Algorithm Development** – Building machine learning or statistical models to make predictions or support decision-making.

5.  **Model Evaluation** – Testing the model’s performance using various evaluation metrics.

6.  **Deployment** – Implementing the model in a real system and monitoring its results.

**Importance of EDA:**\
EDA helps identify trends, outliers, and data distributions within the dataset. This analysis helps determine which model should be used and allows early detection of incorrect data or anomalies.

## **Question:**

Which of the following is a common but incorrect belief about data science?

A\) Data science consists only of statistics.\
B) Data science combines multiple disciplines.\
C) Data science can also be applied to small datasets.\
D) Data science can support decision-making processes.

**Correct Answer:** **A**

## (b)

```{r}
library(dslabs)
data(polls_us_election_2016)

data <- polls_us_election_2016

my_first <- "Ali"
my_birth_year <- 2003

k <- (nchar(my_first) + my_birth_year) %% 15 + 8
k
```

```{r}
if (k %% 2 == 0) {
  head(data, k)
} else {
  tail(data, k)
}
```

```{r}
sum(is.na(data))
```

```{r}
sort(colSums(is.na(data)), decreasing = TRUE)[1:8]
```

```{r}
new_data <- data

for (col in names(new_data)) {

  if (is.numeric(new_data[[col]])) {

    new_data[[col]][is.na(new_data[[col]])] <- my_birth_year + k

  } else if (is.character(new_data[[col]]) | is.factor(new_data[[col]])) {

    new_data[[col]][is.na(new_data[[col]])] <- paste0(my_first, "_", k)

  }

}
```

```{r}
if (k %% 2 == 0) {
  head(new_data, k)
} else {
  tail(new_data, k)
}
```

```{r}
sum(is.na(new_data))
anyNA(new_data)
```
